%% ============================================================
%% 1. INTRODUCTION
%% ============================================================

\newpage
\section{Introduction}

\subsection{Background}

\placeholder{Provide a comprehensive background of the research domain. Discuss the broader context, the current state of knowledge, and relevant developments in the field. Explain why this area of study is important and how it relates to Computer Science and Engineering.}

\placeholder{Include relevant statistics, trends, or real-world applications to establish the significance of the topic. Use citations to support your claims \cite{ref1, ref2}. This section should be 1--2 pages.}

% ===== WRITE YOUR BACKGROUND HERE =====


\subsection{Research Significance}

\placeholder{Explain the academic and practical significance of this research. Describe how the findings could contribute to the field of CSE, benefit society, industry, or specific communities. Highlight the novelty and potential impact of the proposed work.}

% ===== WRITE YOUR RESEARCH SIGNIFICANCE HERE =====


\subsection{Motivation of Research}

\placeholder{Describe what motivated you to pursue this particular research topic. This could include:}
\begin{itemize}[leftmargin=1cm]
    \item \placeholder{Personal interest or observation}
    \item \placeholder{Gaps found in existing literature}
    \item \placeholder{Emerging technological challenges}
    \item \placeholder{Societal needs or real-world problems}
    \item \placeholder{Opportunities identified through preliminary study}
\end{itemize}

% ===== WRITE YOUR MOTIVATION HERE =====
