%% ============================================================
%% 6. LITERATURE REVIEW
%% ============================================================

\newpage
\section{Literature Review}

\placeholder{Conduct a thorough review of existing literature related to your research topic. This section demonstrates your understanding of the current state of research and identifies gaps your work will address. Organize the review thematically or chronologically. Cite at least 15--20 references.}

\subsection{Overview of Related Work}

\placeholder{Summarize key research papers, articles, and studies relevant to your topic. For each work, discuss:}
\begin{itemize}[leftmargin=1cm]
    \item \placeholder{The methodology used}
    \item \placeholder{Key findings and contributions}
    \item \placeholder{Limitations and shortcomings}
\end{itemize}

% ===== WRITE YOUR LITERATURE REVIEW HERE =====
% Example citation usage:
% Smith et al. \cite{ref1} proposed a CNN-based approach that achieved 94\% accuracy...
% However, their method was limited by \cite{ref2}...


\subsection{Comparative Analysis}

\placeholder{Compare and contrast different approaches, models, or techniques used by previous researchers. Use the table below to organize your comparison.}

\begin{table}[H]
\centering
\caption{Comparison of Existing Approaches}
\label{tab:literature_comparison}
\renewcommand{\arraystretch}{1.5}
\begin{tabularx}{\textwidth}{|c|c|X|c|X|}
\hline
\rowcolor{headerblue}
\textbf{Ref.} & \textbf{Year} & \textbf{Method} & \textbf{Accuracy} & \textbf{Limitation} \\
\hline
\cite{ref1} & & & & \\
\hline
\cite{ref2} & & & & \\
\hline
\cite{ref3} & & & & \\
\hline
\cite{ref4} & & & & \\
\hline
\cite{ref5} & & & & \\
\hline
\end{tabularx}
\end{table}


\subsection{Summary of Findings}

\placeholder{Summarize the key findings from the literature review. Highlight:}
\begin{itemize}[leftmargin=1cm]
    \item \placeholder{Common themes and consensus across studies}
    \item \placeholder{Contradictions or conflicting results}
    \item \placeholder{Areas that need further investigation (this leads into Research Gap)}
\end{itemize}

% ===== WRITE YOUR SUMMARY HERE =====
